---
title: "An Exploration with Shiny"
subtitle: "Awakening greatness one project at a time"
author: "Soumya Kalra"
date: "2019/08/11"
output:
  xaringan::moon_reader:
    css: ["default", "rladies", "rladies-fonts"]
    lib_dir: libs
    nature:
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
---

```{r setup, include=FALSE}
options(htmltools.dir.version = FALSE)
#source("analysis.R")
install.packages(c("magrittr", "lubridate", "readr", "dplyr", "ggplot2", "gt", "tidyverse"))
```
# This Talk:

1. Introductions
2. Why Shiny & Why Now? 
3. Basics of Shiny
4. UI with Shiny 
5. Reactive Programming 
6. Future development
7. A few more cool applications
---
# Hi I am Soumya!

- R-Ladies New York Founder
- R/Finance Committee Member
- Quantitative analyst in the public sector
- Do a lot of hands of development in Shiny 

--

- disclaimer: all views in this presentation do not represent the views of my employer and are entirely my own. 

--

## Let's keep talking...
<a href="mailto:sokal1456@gmail.com"><i class="fa fa-paper-plane fa-fw"></i>&nbsp; sokal1456@gmail.com</a><br>
<a href="http://twitter.com/SK_convergence"><i class="fa fa-twitter fa-fw"></i>&nbsp; @SK_convergence</a><br>
---

# What is Shiny?

- Rstudio package authored by Joe Cheng

--

- Web development framework for R

--

- Can be used to build interactive web pages with R

--

- No knowledge of HTML/CSS/JavaScript required

--

- Can share R analysis with any audience type.

---


# Let's get started: Install shiny!

```{r eval=F, echo=T}
# install.pacakges("shiny")
# library(shiny)
runExample("01_hello")
```

```{r eval=T, echo=F}
# install.pacakges("shiny")
# library(shiny)
runExample("01_hello")
```

# Shiny App Basics: Part 1

- Every Shin App is made up of two parts

- UI: a web page that shows the app to the user. UI is HTML using Shiny’s functions and is where the layout of hte app is defined (how the app looks). 

- Server: a computer that powers the app that has the logic of the functionality. 

---

# Shiny App Basics: Part 2

## Shiny Template 

